---
title: "Weight of Fish"
author: "Karen Hernandez"
date: "Year 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch Model

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
PerchData <- filter(fishdata,Species=="Perch") %>% select(-Species)
```

Now build our model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = PerchData,
               nbest = 1,     # 1 best model for each number of predictors
               nvmax = NULL,  # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### The best two regressor model for Perch is Height and Width. This is also the best overall model as measured by adjusted R - squared.


#Bream Model

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
BreamData <- filter(fishdata,Species=="Bream") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = BreamData,
               nbest = 1,     # 1 best model for each number of predictors
               nvmax = NULL,  # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### For the Bream Model the best regressor is Height and then L2-Height.So we can see the adjusted R-squared is 0.9356 for Length 2-height.

```{r}
MODL1 <- lm(Weight~Lenght2+Height,data=BreamData)
summary.lm(MODL1)
```

## Smelt Model

```{r}
# read in the fish data 
fishdata <- read.csv(file="Fish.csv", header=TRUE)
SmeltData <- filter(fishdata,Species=="Smelt") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = SmeltData,
               nbest = 1,     # 1 best model for each number of predictors
               nvmax = NULL,  # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

# Discussion and Final Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
